Final Project

### 2020-11-18 chaloupka_sameshima_wallner_final_project.Rmd

raw_B_long <- raw_B %>% 
 pivot_longer(cols = g:p, names_to = "participant", values_to = "dwell_time")
```

## Create New Dataset Excluding Outliers

@@

seq_fractal_data %>% 
  ggplot(aes(x = sequence_position, y = dwell_time)) +
  facet_wrap(~fractal_type) +
  geom_point(data = new_data_forever, aes(y = mean_dwell_time)) +
  scale_y_continuous(limits = c(0, 1.2)) +
  labs(y = "Dwell Time (s)", x = "Sequence Position")
```

>>>>

raw_B_long <- raw_B %>% 
 pivot_longer(cols = g:p, names_to = "participant", values_to = "dwell_time")
```
<!-- I wonder how hard it would be to make it so each data set had 8 participants. I tried briefly and it didn't like that, as the raw data has 6 and 10 columns, not 8 and 8. -->
## Create New Dataset Excluding Outliers

@@

seq_fractal_data %>% 
  ggplot(aes(x = sequence_position, y = dwell_time)) +
  facet_wrap(~fractal_type) +
  geom_point(data = new_data_forever, aes(y = mean_dwell_time)) +
  scale_y_continuous(limits = c(0, 1.2)) +
  labs(y = "Dwell Time(s)", x = "Sequence Position")
```
<!-- eliminated extra space in Dwell Time(s) -->
